\documentclass[11pt]{article}
\usepackage{config}

\begin{document}

% HEADING
\raggedright
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\huge Marc Franquesa} & \href{mailto:contact@marcfranquesa.com}{contact@marcfranquesa.com}\\
    Undergraduate at CFIS-UPC & \href{https://marcfranquesa.com}{www.marcfranquesa.com} \\
\end{tabular*}

\vspace{3pt}

% EDUCATION
\section{Education}
\place
{CFIS, Polytechnic University of Catalonia (UPC)}{Barcelona, Spain}
{BSc in Mathematics and BSc in Data Science}{Sep 2020 - Jul 2025}
\bulletsPlaceStart
\bulletTitle{CFIS}
{Excellence school at UPC that selects, mentors and gives scholarships to high-performing students at UPC.}
\bulletTitle{Relevant Courses}
{Abstract Algebra, Algorithms \& Data Structures, Probability Theory, Statistics, Information Theory, Signal Processing, Databases, Distributed Systems, Graph Theory, Numerical Analysis, Deep learning, Cryptography \& Computational Finance.}
\bulletTitle{Activites}
{Student board member, organising \href{https://datathon.cat}{Hackathons}.}
\bulletsPlaceEnd


% EXPERIENCE
\section{Experience}
\place
{Massachusetts Institute of Technology (MIT)}{Cambridge, MA}
{Incoming Visiting Student}{Jan 2025 -}
\bulletsPlaceStart
\bulletDesc
{Bachelor’s thesis on causal inference under Prof. Caroline Uhler.}
\bulletsPlaceEnd
% \place
% {Amazon}{Luxembourg, Luxembourg}
% {Incoming Intern}{Jul 2024 - Dec 2024}
\place
{Stanford University}{Remote}
{Research Assistant}{Jan 2024 - Current}
\bulletsPlaceStart
\bulletDesc
{Researching about new applications of deep learning in population genetics.}
\bulletDesc
{Supervised by Prof. Alexander Ioannidis and Dr. Daniel Mas Montserrat.}
\bulletsPlaceEnd
\place
{Polytechnic University of Catalonia (UPC)}{Barcelona, Spain}
{Teaching Assistant}{Feb 2023 - Dec 2023}
\bulletsPlaceStart
\bulletDesc
{First year calculus, algebra \& numerical algebra courses.}
\bulletDesc
{Organising and leading problem-solving sessions, active collaboration with professors.}
\bulletsPlaceEnd

\place
{Esperanto Technologies}{Barcelona, Spain}
{Intern}{Jun 2023 - Sep 2023}
\bulletsPlaceStart
\bulletDesc{
    {Optimized AI performance on their ET-SOC-1 accelerator based on RISC-V technology.}
}
\bulletDesc{
    {Implemented support in C++ for stable diffusion pipelines with a special focus on the diffusion model (U-Net), which made image generation possible.}
}

\bulletsPlaceEnd

\place
{Mango}{Palau-solità i Plegamans, Spain}
{Intern}{Jun 2022 - Jan 2023}
\bulletsPlaceStart
\bulletDesc{
    {Developed a product outlier detection machine learning model in Python.}
}
\bulletDesc{
    {Created an application using generative AI to enhance product design.}
}
\bulletsPlaceEnd


% PROJECTS
\section{Projects}
\bulletsMainStart
\bulletTitleLink{https://fashion-finder-eta.vercel.app}{Fashion Finder \linkIcon}{
    Full stack web application for visualizing and recommending products by querying images on embeddings calculated with FashionCLIP. Made with Next.js (TypeScript) and MongoDB.
}
\bulletTitleLink{https://github.com/marcfranquesa/Junction-2022}{Emosion \githubIcon}{
    Platform that allows users to express and track their mental status, as well as anonymously connect and empathize with other users based on likelihood of improvement.
}
\bulletsMainEnd


% SKILLS & INTERESTS
\section{Skills and Interests}
\bulletsMainStart
\bulletTitle{Technical skills \& tools}{Git, \LaTeX, Docker.}
\bulletTitle{Programming}{Python, C++, R, SQL.}
\bulletTitle{Languages}{English (C2, CPE Certificate), French (B2), Spanish (Native), Catalan (Native).}
\bulletTitle{Hobbies}{Travel, Reading, Puzzles, Ski, Wrestling \& BJJ.}
\bulletsMainEnd

\end{document}
